\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-11-24 conclusions.tex
minor changes to Conclusions

\section{Conclusions \label{sec:conclusions}}
We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. 
%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
\par
In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
%
We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting. 
%
We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.

>>>>

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency larger than that of the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. 
%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
\par
In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
These condition implies that, in the distributed, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk.
